---
title: resume
name: You Shan
surname: Shen
position: "Biostatistics MS"

phone: (612) 618-3240
www: Minneapolis, MN 55414
email:  "shen0464@umn.edu"

output: 
  vitae::markdowncv:
    theme: kjhealy
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

## COURSE WORK EXPERIENCE

 * • Programming 
 *   1. SAS base
 *   2. Advanced R
 *   Data Wrangling: Data Merges, Clean Data (dplyr, tidyr, forcats, stringr, lubridate, purrr::map), Create Functions.
 *   Data visualization: Spatial Visualization(ggplot2, ggplotly), Dashboard(flexdashboard), Table listing (gt, gtExtra).
 *   R markdown, Websites w/R & Github, and HTML.
 * • Statistical Analysis 
 *   1. Generalized linear regression 
 *   2. Poisson regression : handle overdispersion problem
 *   3. Logistic regression : calculate propensity score, effect size and create a contingency table
 *   4. Kaplan-Meier method : redistribution to the right with cancer data.
 *   5. Proportional hazards model
 *   6. Missing Data
 *   7. Bootstrap    
 
 * • Clinical Trials
 *   Randomization, Endpoint, Inclusion and Exclusion Criteria, Non-inferiority, Sample size and Power calculations.


## WORK EXPERIENCE

```{r}
library(tibble)
tribble(
  ~Year, ~Type, ~Desc,
  "2015-2021", "Oncology", "Tri-Service General Hospital (TSGH)-Taipei, Taiwan"
) %>% 
  brief_entries(
    glue::glue("Pharmacist in {Type}"),
    Year, 
    Desc
  )
```
 * •	Poster submission to Taiwan Society of Health-System Pharmacists with colleagues.
   *  Topic: A Case report: pros and cons of Tamoxifen or aromatase inhibitors in male breast cancer. 
   *  Focus on biomarkers (Ki-67, ER, PR) analysis and evaluating the risk of thrombosis of drugs.
 * •	Provide clinicians and patients with the best available evidence when encountering the task of making decisions to achieve patients’ preferable options under Shared Decision Making (SDM).
 * •	Participate in decision-making in marrow transplantation meetings, conduct medicine consultation for cancer patients, and evaluate the cost-effectiveness of pharmacotherapy.

## Education

```{r}

tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Master of Science", "2021-Present", "University of Minnesota", "Minneapolis, MN",
  "Bachelor of Science", "2011-2015", "Chia Nan University of Pharmacy and Science", "Tainan, Taiwan"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)

 
```


## LANGUAGE COMPETENCIES

 * •	English: fluent (speaking, listening, reading, writing)
 * •	Mandarin: native language 
